Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-02 p2/axiom-proof.tex
Final proof

\begin{myclm}[Locality of tree property violations]\mlabel{broken_local}
If two filesystems over $\setn$ have the same values at a node $n$,
$\parentf{n}$ (if exists), and at all children of $n$ (if they exist),
then either both filesystems are broken at $n$, or none of them are.
\end{myclm}

@@

We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
Since the values in the resulting filesystems are the same,
this is only possible if, for an initial non-broken filesystem $\FS$,
one side results in a broken filesystem, and the other side does not.
Without loss of generality, we can assume
$(\cxynv\cc\czwmv)\aFS$ is not broken, but $(\czwmv\cc\cxynv)\aFS$ is.
This means that either $\czwmv\aFS$ is already broken, or it is not, and applying $\cxynv$
breaks the filesystem.

In the former case, the filesystem must be broken at $m$ or $\parentf{m}$.
Since the set of $n$ with its granparent, parent and children; and $m$ with its grandparent, parent and children
are disjunct, we know $\cxynv\aFS$ contains the same values around $m$ as $\aFS$.
This leads to contradiction as from \cref{broken_local} we know
that being broken at $m$ or $\parentf{m}$
... WHAT ABOUT SIBLINGS? ...
while applying $\czwmv$ to $\cxynv\aFS$ on the left-hand side resulted in a working filesystem,
it resulted in a broken filesystem when applied to $\FS$ on the right-hand side.
The proof is similar in the case when applying $\cxynv$ breaks the filesystem on the right-hand side.

>>>>

\begin{myclm}[Locality of tree property violations]\mlabel{broken_local}
If two filesystems over $\setn$ have the same values at a node $n$,
and at all children of $n$ (if they exist),
then either both filesystems are broken at $n$, or none of them are.
\end{myclm}

@@

\begin{proof}
We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
Since the values in the resulting filesystems are the same,
this is only possible if, for an initial non-broken filesystem $\FS$,
one side results in a broken filesystem, and the other side does not.
Without loss of generality, we can assume
$(\cxynv\cc\czwmv)\aFS$ is not broken, but $(\czwmv\cc\cxynv)\aFS$ is.
This means that either $\czwmv\aFS$ is already broken, or it is not, and applying $\cxynv$
breaks the filesystem.

In the former case, based on \cref{broken_local}, 
$\czwmv\aFS$ must be broken at $m$ or $\parentf{m}$, since it only changed at $m$.
Let us look at the first case.
Since $n\indep m$, we know that the parent and children of $m$ have the same value
in $\FS$ as they do in $\cxynv\aFS$. However, this is a contradiction,
as applying $\czwmv$ to $\FS$ leads to a broken filesystem,
but applying it to $\cxynv\aFS$ (from the left side) does not.

Therefore $\czwmv\aFS$ must be broken at $\parentf{m}$.
By definition this means that its value at $\parentf{m}$ cannot be a directory.
Also, reasoning similar to the above shows that it is only possible if $\cxynv$ changes
the environment of $\parentf{m}$, which, since $n\indep m$, is only possible
if $n$ and $m$ are siblings.

Since then the value at $\parentf{n}=\parentf{m}$ is not changed by either command,
we know it cannot be a directory in $\FS$, either, and that therefore
$\FS$ is empty at all children of the parent node.
Since by assumption $\czwmv\aFS$ is broken, $[w]\neq[\empt]$ must hold.
However, this is a contradiction, as this would necessarily mean that
the left side, $\czwmv(\cxynv\aFS)$ must also be broken.

We can proceed in the same fashion if $\czwmv\aFS$ is not broken, but
$(\czwmv\cc\cxynv)\aFS$ is.
\end{proof}

\cref{ax_separate_nobreaks}

\begin{proof}
\end{proof}
